title

### 2018-07-16 01_writing/Schratz_hyperspectral.tex
first draft of introduction (#4)

	% geringerer Zeilenabstand
	%\setlength{\itemsep}{-\parsep}
	\acro{AGB}{Above-Ground Biomass}
	\acro{ANN}{Artificial Neural Network}
	\acro{AUROC}{Area Under the Receiver Operating Characteristics Curve}
	\acro{BRT}{Boosted Regression Trees}
	\acro{CART}{Classification and Regression Trees}
	\acro{CV}{cross-validation}
	\acro{ENM}{Environmental Niche Modeling}
	\acro{FPR}{False Positive Rate}
	\acro{GAM}{Generalized Additive Model}
	\acro{GBM}{Gradient Boosting Machine}
	\acro{GLM}{Generalized Linear Model}
	\acro{ICGC}{Institut Cartografic i Geologic de Catalunya}
	\acro{IQR}{Interquartile Range}
	\acro{WKNN}{Weighted $k$-nearest neighbor}
	\acro{MARS}{Multivariate Adaptive Regression Splines}
	\acro{MEM}{Maximum Entropy Model}
	\acro{NRI}{Normalized Ratio Indeces}
	\acro{OLS}{Ordinary Least Squares}
	\acro{LOWESS}{Locally Weighted Scatter Plot Smoothing}
	\acro{PISR}{Potential Incoming Solar Radiation}
	\acro{RBF}{Radial Basis Function}
	\acro{RF}{Random Forest}
	\acro{RMSE}{Root Mean Square Error}
	\acro{RR}{Ridge Regression}
	\acro{RSS}{Residual Sum of Squares}
	\acro{SDM}{Species Distribution Modeling}
	\acro{SMBO}{Sequential-based Model Optimization}
	\acro{SVM}{Support Vector Machines}
	\acro{TPR}{True Positive Rate}
\end{acronym}

@@

% Explain how remote sensing is used in forestry (potential to map forest health)
Remote sensing data is successfully used in forestry to monitor temporal changes across large areas REFERENCES.
The use of SAR techniques enables scientists to estimate \ac{AGB}.
Forest health is commonly modelled using optical data from multispectral satellites by applying temporal change detections.
With a well-trained model, scientists are able to predict the modelled response to a large area, giving valuable information about the environmental condition of this region.
To model forest health, usually vegetation indices are derived from the band values, i.e. band combinations that are proven to be sensitive to health changes of vegetation.
However, the pool of possible indices is often limited due to a low spectral resolution of freely available data from multispectral sensors.
Also, if the spatial resolution of the data is too coarse (e.g. > 5 m), the value of a pixel contains information of multiple trees and possibly even bare-ground information.
These problems introduce bias into the data which is passed onto the fitted model, leading to non-optimal modeling results.

@@

In this study we will use hyperspectral remote sensing data with a spatial resolution of one meter and 126 spectral bands to model defoliation of \textit{Pinus radiata} trees in northern Spain. 
These trees suffer from infections of invasive pathogens such as \textit{Diplodia sapinea}, \textit{Armillaria} or \textit{Heterobasidion} leading to a spread of cankers or defoliation before the tree dies.
The fungis are assumed to infect the trees through open wounds, possibly caused by hail damage \citep{Iturritxa2014}.
The dieback of these trees, which are mainly used as timber, causes high economic damages in the Iberian Peninsula area.
Remote sensing data in combination with state-of-the-art machine-learning techniques can help to constantly monitor forest health in this region using proxies such as defoliation of the tree crown.
With this information, an increase in defoliation can serve as an early-warning indicator of a possible infection of a plot.

@@

To extract the most information from the available remote sensing data, we not only calculated the most often used vegetation indices (e.g. NDVI) to link against defoliation. 
The narrow bands of the given data enable the calculation of up to 90 vegetation indices.
Additionally, all possible combinations of \ac{NRI} were calculated from the data and supplied to the machine-learning algorithms as predictors.
With their ability to find patterns between the response and its predictors in the data, we hope to increase the predictive accuracy of defoliation based on remote sensing indices.

@@

In this study the following objectives are addressed:

\begin{itemize}
	\item Checking multiple machine-learning algorithms on their ability to model defoliation of \textit{Pinus radiata} trees
	\item Exploration of the most important indices of the model
	\item Prediction of defoliation to plots with unknown levels of defoliation
\end{itemize}

>>>>

	% geringerer Zeilenabstand
	%\setlength{\itemsep}{-\parsep}
	\acro{AGB}{Above-Ground Biomass}
	\acro{ANN}{Artificial Neural Network}
	\acro{AUROC}{Area Under the Receiver Operating Characteristics Curve}
	\acro{BRT}{Boosted Regression Trees}
	\acro{CART}{Classification and Regression Trees}
	\acro{CV}{cross-validation}
	\acro{ENM}{Environmental Niche Modeling}
	\acro{FPR}{False Positive Rate}
	\acro{GAM}{Generalized Additive Model}
	\acro{GBM}{Gradient Boosting Machine}
	\acro{GLM}{Generalized Linear Model}
	\acro{ICGC}{Institut Cartografic i Geologic de Catalunya}
	\acro{IQR}{Interquartile Range}
	\acro{WKNN}{Weighted $k$-nearest neighbor}
	\acro{MARS}{Multivariate Adaptive Regression Splines}
	\acro{MEM}{Maximum Entropy Model}
	\acro{NRI}{Normalized Ratio Indices}
	\acro{OLS}{Ordinary Least Squares}
	\acro{LOWESS}{Locally Weighted Scatter Plot Smoothing}
	\acro{PISR}{Potential Incoming Solar Radiation}
	\acro{RBF}{Radial Basis Function}
	\acro{RF}{Random Forest}
	\acro{RMSE}{Root Mean Square Error}
	\acro{RR}{Ridge Regression}
	\acro{RSS}{Residual Sum of Squares}
	\acro{SAR}{Synthetic Aperture Radar}
	\acro{SDM}{Species Distribution Modeling}
	\acro{SMBO}{Sequential-based Model Optimization}
	\acro{SVM}{Support Vector Machines}
	\acro{TPR}{True Positive Rate}
\end{acronym}

@@

% Explain how remote sensing is used in forestry (potential to map forest health)
Data retrieved from remote sensing satellites is successfully used in forestry to monitor temporal changes across large areas \citep{martinezdelcastilloEvaluationForestCover2015,sextonModelPropagationUncertainty2015}.
The use of \ac{SAR} techniques enables scientists to estimate \ac{AGB} \citep{luSurveyRemoteSensingbased2016, sinhaReviewRadarRemote2015}.
Forest health is commonly assesed using optical data from multi-/hyperspectral satellites by applying temporal change detections \citep{zhangRemoteSensingSeasonal2016}.
With the recent success story of machine-learning methods in the field of remote sensing, modeling techniques such as \ac{RF} are frequently used to model relationships of possible triggers to forest health \citep{belgiuRandomForestRemote2016, laryMachineLearningGeosciences2016, michezClassificationRiparianForest2016}.

With a robust model, predictions of the modelled response to large areas is possible, giving valuable information about the condition of this variable in unknown regions.
To model forest health, usually few variables are extracted based on the spectral signatures of affected and unaffected trees \citep{lelongEvaluationOilPalmFungal2010}. 
However, spectral (vegetation-)indices have shown the potential to contribute valuable information to increase predictive accuracy of forest pathogens \citep{jiangSatellitederivedVegetationIndices2014, adamczykRededgeVegetationIndices2015}.

However, the amount of possible (vegetation-)indices that could be calculated is often limited due to a low spectral resolution of freely available data from optical multispectral sensors (e.g. Sentinel-2).
Also, there is currently no free data available from hyperspectral sensors that could be used for such studies (after the decommission of the EO-1 Hyperion satellite).
If the spatial resolution of the data is too coarse (e.g. $> 5 m$), the value of a pixel usually contains information from multiple trees and possibly even bare-ground information.
This makes the resulting information almost useless to be used for forest health monitoring on a tree level.

@@

In this study we will use hyperspectral data with a spatial resolution of one meter and 126 spectral bands to model the health status of Monterey Pine (\textit{Pinus radiata}) plantations in northern Spain. 
The trees in the study area suffer from infections of invasive pathogens such as \textit{Diplodia sapinea}, \textit{Fusarium circinatum} \textit{Armillaria mellea} or \textit{Heterobasidion annosum} leading to a spread of cankers or defoliation before the tree dies \citep{mesanzaNativeRhizobacteriaBiocontrol2016, iturritxaBiocontrolFusariumCircinatum2017}.
In-situ measurements of defoliation on a tree level are used as a proxy to model tree health.
The fungis are assumed to infect the trees through open wounds, possibly caused by previous hail damage \citep{Iturritxa2014}.
The dieback of these trees, which are mainly used as timber, causes high economic damages \citep{ganleyGlobalClimaticRisk2009}.
Hyperspectral remote sensing data in combination with state-of-the-art machine-learning techniques is used to help monitoring the health status in this region by early detecting affected trees/plots.

@@

To extract the most information from the available remote sensing data, we not only calculated the most common vegetation indices like \textit{NDVI} to link against defoliation but all possible ones within the spectral region of the data (400 nm - 1000 nm) that were implemented in the \textit{hsdar} package in R \citep{hsdar}.
Additionally, all possible combinations of \ac{NRI} were calculated from the data and supplied to a selection of machine-learning algorithms as predictors.

@@

Specifically the following objectives are addressed:

\begin{itemize}
	\item Comparison of multiple algorithms on their performance to model defoliation of \textit{Pinus radiata} trees using highly-correlated indices
	\item Exploration of the most important indices of the best performing model
	\item Prediction of defoliation to \textit{Pinus radiata} plots with an unknown defoliation level
\end{itemize}
